CommonMind Consortium: DLPFC

### 2020-09-20 combined_analysis/diff.networks.Rmd
Update diff networks

	ggplot(res, aes(Test, -log10(PValue))) + geom_bar(stat="identity", fill=res$Geneset[1]) + coord_flip() + theme_bw() + theme(aspect.ratio=1, plot.title = element_text(hjust = 0.5))  + scale_y_continuous(expand=c(0,0)) + ggtitle(module)
}) 
plot_grid(plotlist = figList, ncol=1)
```

@@

## DE enrichment
```{r cameraPR.Dx}
res_enrich_DE = enrich_module_DE( df_module.Dx )

>>>>

	lim = max(-log10(res$PValue))

	ggplot(res, aes(Test, -log10(PValue))) + geom_bar(stat="identity", fill=res$Geneset[1]) + coord_flip() + theme_bw() + theme(aspect.ratio=1, plot.title = element_text(hjust = 0.5))  + scale_y_continuous(expand=c(0,0), lim=c(0, lim*1.05)) + ggtitle(module) + geom_hline(yintercept=-log10(0.05), color="red", linetype="dashed")
}) 
plot_grid(plotlist = figList, ncol=1)
```

@@

## DE enrichment
```{r cameraPR.Dx, fig.width=7, fig.height=20}
res_enrich_DE = enrich_module_DE( df_module.Dx )
